Draft Final Report: Measles risk assessment, modelling, and benefit--cost analyses for New Zealand

### 2015-04-24 draftfinalreport_v3.Rnw
update rest of figures to drop '2013' from area unit in captions etc.

 \vspace{5mm} %5mm vertical space
\begin{table}
<<include=FALSE,echo=FALSE,results=tex>>=
latex(table_nir_mmr, file="", table.env=FALSE,rowname=NULL)
@
\caption{Summary of the proportion of 2006--2014 birth cohorts vaccinated against measles-mumps-rubella (MMR) dose 1 and MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12006}, \autoref{fig:fig22006}, \autoref{fig:fig12007}, \autoref{fig:fig22007}, \autoref{fig:fig12008}, \autoref{fig:fig22008}, \autoref{fig:fig12009}, \autoref{fig:fig22009}, \autoref{fig:fig12010}, \autoref{fig:fig22010}, \autoref{fig:fig12011}, \autoref{fig:fig22011}, \autoref{fig:fig12012}, \autoref{fig:fig22012}, \autoref{fig:fig12013}, \autoref{fig:fig22013}, \autoref{fig:fig12014}, and \autoref{fig:fig22014}.}
\label{table:tab_mmr_nir}
\end{table}

\begin{sidewaysfigure}
   \begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2006.pdf}
    \end{center}
    \caption{Proportion of the New Zealand population born in 2006 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12006}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22006)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22006[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22006}.}
% \label{table:tab22006}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
\includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2006.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2006 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22006}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12007)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12007[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12007}.}
% \label{table:tab12007}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
\includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2007.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2007 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig12007}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22007)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22007[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22007}.}
% \label{table:tab22007}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2007.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2007 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22007}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12008)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12008[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12008}.}
% \label{table:tab12008}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2008.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2008 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig12008}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22008)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22008[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22008}.}
% \label{table:tab22008}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2008.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2008 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22008}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12009)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12009[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12009}.}
% \label{table:tab12009}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2009.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2009 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12009}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22009)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22009[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22009}.}
% \label{table:tab22009}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2009.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2009 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig22009}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12010)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12010[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12010}.}
% \label{table:tab12010}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2010.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2010 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12010}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22010)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22010[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22010}.}
% \label{table:tab22010}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2010.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2010 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig22010}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12011)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12011[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2011 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12011}.}
% \label{table:tab12011}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2011.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2011 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12011}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22011)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22011[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2011 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22011}.}
% \label{table:tab22011}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2011.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2011 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig22011}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12012)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12012[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2012 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12012}.}
% \label{table:tab12012}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2012.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2012 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12012}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22012)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22012[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2012 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22012}.}
% \label{table:tab22012}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2012.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2012 vaccinated against measles using MMR2 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22012}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12013)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12013[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR1 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12013}.}
% \label{table:tab12013}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2013.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2013 vaccinated against measles using MMR1 in each 2013 area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig12013}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22013)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22013[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR2 across the 2013 area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22013}.}
% \label{table:tab22013}
% \end{table}

>>>>

 \vspace{5mm} %5mm vertical space
\begin{table}
<<include=FALSE,echo=FALSE,results=tex>>=
latex(table_nir_mmr, file="", table.env=FALSE,rowname=NULL)
@
\caption{Summary of the proportion of 2006--2014 birth cohorts vaccinated against measles-mumps-rubella (MMR) dose 1 and MMR2 across area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12006}, \autoref{fig:fig22006}, \autoref{fig:fig12007}, \autoref{fig:fig22007}, \autoref{fig:fig12008}, \autoref{fig:fig22008}, \autoref{fig:fig12009}, \autoref{fig:fig22009}, \autoref{fig:fig12010}, \autoref{fig:fig22010}, \autoref{fig:fig12011}, \autoref{fig:fig22011}, \autoref{fig:fig12012}, \autoref{fig:fig22012}, \autoref{fig:fig12013}, \autoref{fig:fig22013}, \autoref{fig:fig12014}, and \autoref{fig:fig22014}.}
\label{table:tab_mmr_nir}
\end{table}

\begin{sidewaysfigure}
   \begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2006.pdf}
    \end{center}
    \caption{Proportion of the New Zealand population born in 2006 vaccinated against measles using MMR1 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12006}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22006)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22006[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR2 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22006}.}
% \label{table:tab22006}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
\includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2006.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2006 vaccinated against measles using MMR2 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22006}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12007)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12007[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR1 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12007}.}
% \label{table:tab12007}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
\includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2007.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2007 vaccinated against measles using MMR1 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig12007}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22007)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22007[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2007 birth cohort vaccinated against MMR2 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22007}.}
% \label{table:tab22007}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2007.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2007 vaccinated against measles using MMR2 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22007}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12008)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12008[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR1 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12008}.}
% \label{table:tab12008}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2008.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2008 vaccinated against measles using MMR1 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig12008}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22008)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22008[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2008 birth cohort vaccinated against MMR2 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22008}.}
% \label{table:tab22008}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2008.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2008 vaccinated against measles using MMR2 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22008}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12009)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12009[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR1 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12009}.}
% \label{table:tab12009}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2009.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2009 vaccinated against measles using MMR1 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12009}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22009)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22009[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2009 birth cohort vaccinated against MMR2 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22009}.}
% \label{table:tab22009}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2009.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2009 vaccinated against measles using MMR2 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig22009}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12010)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12010[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR1 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12010}.}
% \label{table:tab12010}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2010.pdf}
\end{center}
    \caption{Proportion of the New Zealand population born in 2010 vaccinated against measles using MMR1 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12010}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22010)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22010[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2010 birth cohort vaccinated against MMR2 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22010}.}
% \label{table:tab22010}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2010.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2010 vaccinated against measles using MMR2 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig22010}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12011)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12011[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2011 birth cohort vaccinated against MMR1 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12011}.}
% \label{table:tab12011}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2011.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2011 vaccinated against measles using MMR1 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12011}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22011)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22011[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2011 birth cohort vaccinated against MMR2 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22011}.}
% \label{table:tab22011}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2011.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2011 vaccinated against measles using MMR2 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig22011}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12012)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12012[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2012 birth cohort vaccinated against MMR1 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12012}.}
% \label{table:tab12012}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2012.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2012 vaccinated against measles using MMR1 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
%\end{center}
\label{fig:fig12012}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22012)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22012[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2012 birth cohort vaccinated against MMR2 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22012}.}
% \label{table:tab22012}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR2_NIR_2012.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2012 vaccinated against measles using MMR2 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig22012}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t12013)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t12013[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR1 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig12013}.}
% \label{table:tab12013}
% \end{table}

\begin{sidewaysfigure}
\begin{center}
    \includegraphics[width=0.9\textwidth]{nir_census_MMR1_NIR_2013.pdf}
 \end{center}
    \caption{Proportion of the New Zealand population born in 2013 vaccinated against measles using MMR1 in each area unit. Note no adjustment is made for vaccine efficacy. The histogram shows the frequency of the proportion vaccinated across the country's area units with 95\% shown in red and the median for the cohort shown in orange. See \autoref{table:tab_mmr_nir} and the supplementary data for details.}
% \end{center}
\label{fig:fig12013}
\end{sidewaysfigure}

%  \vspace{5mm} %5mm vertical space
% \begin{table}
% <<include=FALSE,echo=FALSE,results=tex>>=
% colnames(t22013)<-c("Min","1st Q","Median","Mean","3rd Q","Max","NA")
% latex(t22013[1:7], file="", table.env=FALSE,rowname=NULL)
% @
% \caption{Summary of the proportion of 2006 birth cohort vaccinated against MMR2 across the area units. Area units are aggregations of meshblock data. See \autoref{fig:fig22013}.}
% \label{table:tab22013}
% \end{table}
